Supporting Infromation

### 2022-02-22 Manuscript/10-Supplementary.Rmd
Update Support Info
Add lnr sim tables to supplementary

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newcommand{\tp}{*}
\newcommand{\pr}{\text{Pr}}

@@

\subsection{Supplementary Information 1: EM-IWLS Algorithm for Fitting Bayesian Hierarchical Additive Models}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
\newcommand{\tp}{*}
\newcommand{\pr}{\text{Pr}}
\newcommand{\bs}[1]{\boldsymbol{#1}}

@@

\subsection{Supplementary Information 2: EM-IWLS Algorithm for Fitting Bayesian Hierarchical Additive Models}

@@

\subsection{Supplementary Information 3: Predictive Performance of Linear Simulations}
\input{Manuscript/Tabs/sim_lnr_gaus_tab.tex}
\clearpage
\input{Manuscript/Tabs/sim_lnr_binom_tab.tex}
